Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-01 paper_comparison/paper_comparison/paper_comparison.Rmd
update background

To scrutinize the relationship between residuals, predicted values and each of the explanatory variables, it is recommend to plot them on a scatter plot. In general, one will check whether there is any noticeable pattern to determine if the model is well-behaved. However, it is a very difficult task for a human judge, though to make a decision that there's nothing there. It is especially common, particularly among new data analysts to report patterns when an experienced data analyst might quickly conclude that there are none. Generally, one looks for departures from nothingness like nonlinear dependency or heteroskedasticity. It is also possible to conduct a hypothesis test for non-linear dependence [@ramsey_tests_1969], and also use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are referred to as standard residual plots in @cook1982residuals. As suggested by @cook1982residuals, these kinds of diagnostic plots are commonly used to identify patterns that are indicative of nonconstant error variance or non-linearity. Raw residuals and studentized residuals are the two most frequently used residuals in standard residual plots. The debt on which type of residuals should be used is always present. While raw residuals are the most common computer regression software package output, by applying a scaling factor, the ability to reveal nonconstant error variance in standard residual plots will often be enhanced by studentized residuals in small sample size [@gunst1980regression]. As a two-dimensional representation of a model in a $p$-dimensional space, standard residual plots project data points onto the variable of the horizontal axis, which is a vector in $p$-dimensional space. Observations with the same projection will be treated as equivalent as they have the same abscissa. Consequently, standard residual plots are often useful in revealing model inadequacies in the direction of the variable of the horizontal axis but could be inadequate for detecting patterns in other directions, especially in those perpendicular to the variable of the horizontal axis. Hence, in practice, multiple standard residual plots with different horizontal axes will be examined [@cook1982residuals]. Overlapping data points is another general issue in scatter plots not limited to standard residual plots, which often makes plots difficult to interpret because visual patterns are concealed. Thus, for a relatively large sample size, @cleveland1975graphical suggests the use of robust moving statistics as reference lines to give aid to the eye in seeing patterns, which nowadays, are usually replaced with a spline or local polynomial regression line.

>>>>

To scrutinize the relationship between residuals, predicted values and each of the explanatory variables, it is recommend to plot them on a scatter plot. In general, the model is well-behaved if there is any visual discoverable pattern. However, it is a very difficult task for a human judge, though to make a decision that there's nothing there. It is especially common, particularly among new data analysts to report patterns when an experienced data analyst might quickly conclude that there are none. Generally, one looks for departures from nothingness like non-linear dependency or heteroskedasticity. It is also possible to conduct hypothesis tests for non-linear dependence [@ramsey_tests_1969], and also use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

```{r}
mod <- poly_model(include_z = FALSE, sigma = 0.25)
dat <- mod$gen(300)
patchwork::wrap_plots(mod$plot(dat, theme = theme_light()) + ggtitle("Good residuals"),
                      mod$plot(mod$set_prm("include_z", TRUE)$gen(300, computed = select(dat, x, e)), theme = theme_light()) + ggtitle("Non-linearity"),
                      mod$plot(heter_model(b = 64)$gen(300, computed = select(dat, x, e)), theme = theme_light()) + ggtitle("Heteroskedasticity"),
                      mod$plot(heter_model(b = 0, e = rand_lognormal(sigma = 0.5))$gen(300, computed = select(dat, x)), theme = theme_light()) + ggtitle("Non-normality"))
```

Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are referred to as standard residual plots in @cook1982residuals. As suggested by @cook1982residuals, these kinds of diagnostic plots are commonly used to identify patterns that are indicative of non-linearity or nonconstant error variance.

Raw residuals and studentized residuals are the two most frequently used residuals in standard residual plots. The debt on which type of residuals should be used is always present. While raw residuals are the most common computer regression software package output, by applying a scaling factor, the ability to reveal nonconstant error variance in standard residual plots will often be enhanced by studentized residuals in small sample size [@gunst1980regression]. As a two-dimensional representation of a model in a $p$-dimensional space, standard residual plots project data points onto the variable of the horizontal axis, which is a vector in $p$-dimensional space. Observations with the same projection will be treated as equivalent as they have the same abscissa. Consequently, standard residual plots are often useful in revealing model inadequacies in the direction of the variable of the horizontal axis but could be inadequate for detecting patterns in other directions, especially in those perpendicular to the variable of the horizontal axis. Hence, in practice, multiple standard residual plots with different horizontal axes will be examined [@cook1982residuals]. Overlapping data points is another general issue in scatter plots not limited to standard residual plots, which often makes plots difficult to interpret because visual patterns are concealed. Thus, for a relatively large sample size, @cleveland1975graphical suggests the use of robust moving statistics as reference lines to give aid to the eye in seeing patterns, which nowadays, are usually replaced with a spline or local polynomial regression line.

### 2022-09-01 paper_comparison/paper_comparison/paper_comparison.tex
update background

Residuals might be plotted, as a histogram or quantile-quantile plot to
examine the distribution. Using classical linear regression model as an
example, if the distribution is symmetric and unimodal, then it is
well-behaved. But if the distribution is skewed, bimodal, multimodal, or
even contains outliers, there is cause for concern. It is also possible
to conduct a goodness of fit test to examine the distribution of
residuals, such as Shapiro-Wilk Normality test
\citep{shapiro1965analysis}.

To examine the relationship between residuals, predicted values and each
of the explanatory variables, it is recommend to plot them on a scatter
plot with residuals on the y-axis. This type of plot is usually called
residual plot. In general, one will check whether there is any
noticeable pattern to determine if the model is well-behaved. However,
it is a very difficult task for a human judge, though to make a decision
that there's nothing there. It is especially common, particularly among
new data analysts to report patterns when an experienced data analyst
might quickly conclude that there are none. Generally, one looks for
departures from nothingness like nonlinear dependency or
heteroskedasticity. It is also possible to conduct a hypothesis test for
non-linear dependence \citep{ramsey_tests_1969}, and also use a
Breusch-Pagan test \citep{breusch_simple_1979} for heteroskedasticity.

@@

Graphical summaries in which residuals are plotted against fitted values
or other functions of the predictor variables that are approximately
orthogonal to residuals are referred to as standard residual plots in
\citet{cook1982residuals}. As suggested by \citet{cook1982residuals},
these kinds of diagnostic plots are commonly used to identify patterns
that are indicative of nonconstant error variance or non-linearity. Raw
residuals and studentized residuals are the two most frequently used
residuals in standard residual plots. The debt on which type of
residuals should be used is always present. While raw residuals are the
most common computer regression software package output, by applying a
scaling factor, the ability to reveal nonconstant error variance in
standard residual plots will often be enhanced by studentized residuals
in small sample size \citep{gunst1980regression}. As a two-dimensional
representation of a model in a \(p\)-dimensional space, standard
residual plots project data points onto the variable of the horizontal
axis, which is a vector in \(p\)-dimensional space. Observations with
the same projection will be treated as equivalent as they have the same
abscissa. Consequently, standard residual plots are often useful in
revealing model inadequacies in the direction of the variable of the
horizontal axis but could be inadequate for detecting patterns in other
directions, especially in those perpendicular to the variable of the
horizontal axis. Hence, in practice, multiple standard residual plots
with different horizontal axes will be examined
\citep{cook1982residuals}. Overlapping data points is another general
issue in scatter plots not limited to standard residual plots, which
often makes plots difficult to interpret because visual patterns are
concealed. Thus, for a relatively large sample size,
\citet{cleveland1975graphical} suggests the use of robust moving
statistics as reference lines to give aid to the eye in seeing patterns,
which nowadays, are usually replaced with a spline or local polynomial
regression line.

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-12-1.pdf}

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-15-1.pdf}

@@

>>>>

Residuals might be plotted, as a histogram or quantile-quantile plot to
examine the distribution. Using the classical linear regression model as
an example, if the distribution is symmetric and unimodal, it is
well-behaved. But if the distribution is skewed, bimodal, multimodal, or
even contains outliers, there is cause for concern. Conducting a
goodness of fit test is an alternative method for inspecting the
distribution, such as the Shapiro-Wilk Normality test
\citep{shapiro1965analysis}.

To scrutinize the relationship between residuals, predicted values and
each of the explanatory variables, it is recommend to plot them on a
scatter plot. In general, the model is well-behaved if there is any
visual discoverable pattern. However, it is a very difficult task for a
human judge, though to make a decision that there's nothing there. It is
especially common, particularly among new data analysts to report
patterns when an experienced data analyst might quickly conclude that
there are none. Generally, one looks for departures from nothingness
like non-linear dependency or heteroskedasticity. It is also possible to
conduct hypothesis tests for non-linear dependence
\citep{ramsey_tests_1969}, and also use a Breusch-Pagan test
\citep{breusch_simple_1979} for heteroskedasticity.

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-6-1.pdf}

Graphical summaries in which residuals are plotted against fitted values
or other functions of the predictor variables that are approximately
orthogonal to residuals are referred to as standard residual plots in
\citet{cook1982residuals}. As suggested by \citet{cook1982residuals},
these kinds of diagnostic plots are commonly used to identify patterns
that are indicative of non-linearity or nonconstant error variance.

Raw residuals and studentized residuals are the two most frequently used
residuals in standard residual plots. The debt on which type of
residuals should be used is always present. While raw residuals are the
most common computer regression software package output, by applying a
scaling factor, the ability to reveal nonconstant error variance in
standard residual plots will often be enhanced by studentized residuals
in small sample size \citep{gunst1980regression}. As a two-dimensional
representation of a model in a \(p\)-dimensional space, standard
residual plots project data points onto the variable of the horizontal
axis, which is a vector in \(p\)-dimensional space. Observations with
the same projection will be treated as equivalent as they have the same
abscissa. Consequently, standard residual plots are often useful in
revealing model inadequacies in the direction of the variable of the
horizontal axis but could be inadequate for detecting patterns in other
directions, especially in those perpendicular to the variable of the
horizontal axis. Hence, in practice, multiple standard residual plots
with different horizontal axes will be examined
\citep{cook1982residuals}. Overlapping data points is another general
issue in scatter plots not limited to standard residual plots, which
often makes plots difficult to interpret because visual patterns are
concealed. Thus, for a relatively large sample size,
\citet{cleveland1975graphical} suggests the use of robust moving
statistics as reference lines to give aid to the eye in seeing patterns,
which nowadays, are usually replaced with a spline or local polynomial
regression line.

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-13-1.pdf}

@@

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-19-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-20-1.pdf}
